---
title: "MD6 Extra"
format: html
editor: visual
embed-resources: true
---

## HW 6.2

```{r}
library(tidyverse)
library(moderndive)
theme_set(theme_minimal())
```

```{r}
data(bikes, package = "bayesrules")
glimpse(bikes)
```

## Question 0

-   500 rows

-   Each row is the ride data for one day

-   January 2011 - December 2012

-   Highest amount of rides in a day is 6946

-   Highest wind speed is 34mph

## Question 1

```{r}
get_correlation(rides ~ temp_feel,
                data = bikes) %>% round(2)
```

The correlation between number of rides and what the temperature feels like in Fahrenheit is 0.58

```{r}
get_correlation(rides ~ windspeed,
                data = bikes) %>% round(2)
```

The correlation between the number of rides and windspeed in mph is -0.19

## Question 2

```{r}
bikes <- bikes %>% 
  mutate(wind_kph = windspeed * 1.61)
```

```{r}
get_correlation(windspeed ~ wind_kph,
                data = bikes)
```

The correlation between wind speed in mph and wind speed in kph is 1. This is because it is simply a unit conversion as every kilometer is 1.6x of its mph point and the same goes for the opposite way.

## Question 3

```{r}
mph1 <- lm(rides ~ windspeed,
                data = bikes)
get_regression_table(mph1) %>% 
  select(term, estimate)
```

```{r}
kph1 <- lm(rides ~ wind_kph,
                data = bikes)
get_regression_table(kph1) %>% 
  select(term, estimate)
```

Both intercepts are the same at 4205.065. The intercept is relating to when rides=0 and 0 kph = 0 mph, so this makes sense when rides is = 0. However, the slopes are different as they are separated by a factor of 1.61 as seen in the coefficients in the conversion. -55.523 / -34.48600 = 1.6100

## Question 4

Rides = 4205 - 55.523 kph = 3094. 6 rides rounded to 3095 riders on a 20kph day.

Rides = 4205 - 34.486 mph = 3515. 3 riders rounded to 3515 riders on a 20mph day.

## Question 5

```{r}
bikes <- bikes %>% 
  mutate(temp_c = (temp_feel-32)*(5/9))
```

```{r}
mult_model <- lm(rides ~ wind_kph + temp_c,
                 data = bikes)
get_regression_table(mult_model) %>% 
  select(term, estimate)
```

C = (F-32) \* \\frac{5}{9}

For a 1 degree Celsius increase in temperature, the model expects 143 increase in rides.

For a 1 kph increase in wind speed, the model expects a decrease in 20 rides.

The intercept tells us the expected rides of a still day with a temperature of 0C / 32F is 942.

## Question 6

```{r}
pred_df <- tibble(
  situation = 1:3,
  temp_c = c(25, 15, 10),
  wind_kph = c(15, 5, 40)
)
```

```{r}
predicted_rides <- predict(mult_model, newdata = pred_df)
print(pred_df)
```

4226 riders for situation 1

2992 riders for situation 2

1581 riders for situation 3

## Question 7

```{r}
bikes <- bikes %>% mutate(weekend = as.factor(weekend))
weekend <- lm(rides ~ wind_kph + weekend + temp_c,
                    data = bikes)
get_regression_table(weekend) %>%
  select(term, estimate)
```

The weekend model coefficient above tells us that there will be 714 fewer riders on a weekend than a weekday.

## Question 8

```{r}
library(ggeffects)
predictions <- ggpredict(weekend,
                         terms = c("weekend"),
                         ci_level = NA) # don't think about confidence intervals yet (soon!)
predictions
```

When holding the temperature and wind speed average, the expected riders for a weekend is 2970 and the weekday is 3683.

## Question 9

```{r}
bikerides <- predict(weekend)
residuals <- bikes$rides - bikerides
broom::tidy(residuals)
residuals
```

|              |
|-------------:|
| -3490.347507 |

The largest absolute residual was -3490 on day 439. This day there were only 20 rides due to a Hurricane coming in and major streets being shut down.
