---
title: "MD6"
format: html
editor: visual
embed-resources: true
---

## MD6

```{r}
library(tidyverse)
# Set our ggplot theme from the outset
theme_set(theme_light())
# Read in the data 
gender_employment <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/gender_employment.csv")

# Glimpse at the data 
glimpse(gender_employment)
```

```{r}
#| warning: false
gender_employment%>% 
  ggplot(aes(x = year, y = wage_percent_of_male)) +
  geom_jitter(alpha = 0.1) + 
  geom_smooth(method = "lm") + 
  labs(title = "Women's earnings with respect to men's", 
       y = "% of Men's Income", 
       x = "Year")
```

## Question 1

```{r}
gender_employment <- gender_employment %>% 
  mutate(major_category = as.factor(major_category), 
         major_category = relevel(major_category, ref = "Management, Business, and Financial"))

```

```{r}
parallel_model <- lm(wage_percent_of_male ~ year + major_category,
                     data = gender_employment)
broom::tidy(parallel_model)
```

Looking at the data, I see that the every year the wage percentage of male increases by a 0.192 % point.

{y} = -306.7183854 + 0.1922095(\\text{year}) + 6.3194352(\\text{CES}) + 5.7562764(\\text{ELCSAM}) + 5.5209507(\\text{HPT}) + 4.9146651(\\text{NRCM}) - 1.3112146(\\text{PTMM}) + 3.3261175(\\text{SO}) + 6.0769722(\\text{S})\$\$

{y} = -306.7183854 + 0.1922095(2015) + 3.3261175(1) = 83.90987

In 2015, the Sales and Office occupations hit 93.91% male income.

{y} = -306.7183854 + 0.1922095(2016) + 6.08(1) = 86.85597

In 2016, the Service occupations had 86.86% of male income

## Question 2

```{r}
#| warning: false
gender_employment%>% 
  ggplot(aes(x = year,
             y = wage_percent_of_male,
             group = major_category)) +
  geom_smooth(method = "lm",
              se = FALSE) + 
  labs(title = "Women's earnings with respect to men's", 
       y = "% of Men's Income", 
       x = "Year")
```

We cannot use this parallel trends assumption because of the discrepancy across industrial categories.

## Question 3

```{r}
interaction_model <- lm(wage_percent_of_male ~ year*major_category,
                        data = gender_employment)
broom::tidy(interaction_model)
```

{y} = -1370.4719187 + 0.7202561(2016) + 1002.8532317(1) - 0.4946783(2016)(1) = 87.14616

In 2016, the CES is 87.15% of male income.

{y} = -1370.4719187 + 0.7202561(2016) + 2137.6501474(1) - 1.0581075(2016)(1) = 86.06981

In 2016, Service jobs made 86.07% of male income. The main difference requires two switches instead of just one in the previous model.

## Question 4

A model that assumes parallel trends can help when there is not enough data as the results would be variable and not very accurate. Also, it can help using a baseline model for the data set.

## Question 5

```{r}
simple_fit <- lm(wage_percent_of_male ~ year,
                 data = gender_employment)
broom::tidy(simple_fit)
```

Every year that increases, the wage percent of male increases by 0.2% points.

```{r}
gender_employment %>% 
  select(year, wage_percent_of_male, percent_female) %>% 
  cor(use = "complete.obs")
```

The wage percent of male increases by 0.24% points per year while the percent female increases by 0.005 of one percentage points per year.

```{r}
multiple_fit <- lm(wage_percent_of_male ~ year*percent_female,
                   data = gender_employment)
broom::tidy(multiple_fit)
```

This is not what I expected. I did expect to see the percent of women working in an occupation to be growing at 10% points per year. I expected this number to be lower, so this data is very useful and interesting.

## Question 6

R squared tells us how much variation there is of the dependent explained by the independent variable in the model we have.

```{r}
simple_glanced <- broom::glance(simple_fit)
simple_glanced$r.squared
```

```{r}
multiple_glanced <- broom::glance(multiple_fit)
multiple_glanced$r.squared
```

R squared is larger in the multiple regression. We can derive from this that there is a larger amount of the dependent variable that relies on the independent variable, which makes it the appropriate fit for this relationship between year and percentage_female.
